### 2020-01-15 defesa/tex/chapter/mcer.tex
wip

	\begin{equation}
	\Phi_j(u, v) := \{\theta \in [0, \pi) : \theta \textnormal{ is a } (E_j,u,v)\textnormal{-feasible angle}\}.
	\end{equation}
\end{definicao}

@@

\begin{lema}\label{lema:3pnts}
Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER. Then, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|>2$, at least one of the two cases is true:

	\begin{enumerate}[label=(\alph*)]
		\item There is an equivalent solution $(Q', \Theta')$, such that $|\Pp\cap \partial E_j(q'_j, \theta'_j)| \ge 3$.\label{lema:3pnts_a}

		\item There is $\{u, v\}\subset\Pp \cap E_j(q_j^*, \theta_j^*)$, such that for any $\theta\in\Phi_j(u,v)$, there is $q\in\R^2$, such that $\{u, v\} \subset \partial E_j(q, \theta)$ and $\Pp \cap E_j(q^*_j, \theta^*_j) = \Pp \cap E_j(q, \theta)$. \label{lema:3pnts_b}
	\end{enumerate}
\end{lema}

\begin{proof}
	We are going to prove that if \autoref{lema:3pnts}\ref{lema:3pnts_a} is false, then \autoref{lema:3pnts}\ref{lema:3pnts_b} is true; and if \autoref{lema:3pnts}\ref{lema:3pnts_b} is false, then \autoref{lema:3pnts}\ref{lema:3pnts_a} is true.

@@

	Suppose that \autoref{lema:3pnts}\ref{lema:3pnts_a} is false.  
	According to \autoref{lema:mce_2b}, there exists $\{u, v\} \subset \Pp$, such that an equivalent optimal solution exists with $u, v$ on the border of $E_j$.

>>>>

	\begin{equation}
	\Phi_j(u, v) := \{\theta \in [0, \pi] : \theta \textnormal{ is a } (E_j,u,v)\textnormal{-feasible angle}\}.
	\end{equation}
\end{definicao}

@@

\begin{lema}\label{lema:3pnts}
Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER. Then, for any $E_j \in \E$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|>2$, the following statements are equivalent:

	\begin{enumerate}[label=(\alph*)]
		\item $|\Pp\cap \partial E_j(q'_j, \theta'_j)| < 3$, for any equivalent solution $(Q', \Theta')$, \label{lema:3pnts_a}

		\item There is $\{u, v\}\subset\Pp \cap E_j(q_j^*, \theta_j^*)$, such that for any $\theta'\in\Phi_j(u,v)$, there is $q\in\R^2$, such that $\{u, v\} \subset \partial E_j(q, \theta)$ and $\Pp \cap E_j(q^*_j, \theta^*_j) = \Pp \cap E_j(q, \theta)$.\label{lema:3pnts_b}
	\end{enumerate}
\end{lema}

\begin{proof}
	To make the text more clear, let $A=\Pp\cap E_j(q^*_j, \theta^*_j)$.

	$\Rightarrow$

	According to \autoref{lema:mce_2b}, there exists $\{u, v\} \subset \Pp$, such that an equivalent optimal solution $(Q', \Theta^*)$ exists with $u, v$ on the border of $E_j(q_j', \theta_j^*)$. Therefore, $\theta_j^*\in\Phi_j(u,v)$.

	Suppose that $|\Phi_j(u,v)|>1$

	We are going to prove that if \autoref{lema:3pnts}\ref{lema:3pnts_a} is false, then \autoref{lema:3pnts}\ref{lema:3pnts_b} is true; and if \autoref{lema:3pnts}\ref{lema:3pnts_b} is false, then \autoref{lema:3pnts}\ref{lema:3pnts_a} is true.

@@

	Suppose that \autoref{lema:3pnts}\ref{lema:3pnts_a} is false.
